Tensor anisotropy as a tracer of cosmic voids

### 2015-06-20 cosmic_voids.tex
including references

\bibliographystyle{mn2e}
\bibliography{references}

>>>>

\bibliographystyle{mn2e}
%\bibliography{references}
\begin{thebibliography}{}

\bibitem[\protect\citeauthoryear{{Abazajian}, et al. \& {(the SDSS
  Collaboration)}}{{Abazajian} et~al.}{2003}]{Abazajian03}
{Abazajian} K.,  et al.   {(the SDSS Collaboration)} 2003, \aj, 126, 2081

\bibitem[\protect\citeauthoryear{{Alonso}, {Eardley} \& {Peacock}}{{Alonso}
  et~al.}{2015}]{Alonso2015}
{Alonso} D.,  {Eardley} E.,    {Peacock} J.~A.,  2015, \mnras, 447, 2683

\bibitem[\protect\citeauthoryear{{Basser}}{{Basser}}{1995}]{Basser95}
{Basser} P.,  1995, NMR in Biomedical Imaging, 8, 333

\bibitem[\protect\citeauthoryear{{Bertschinger}}{{Bertschinger}}{1985}]{Bertschinger85}
{Bertschinger} E.,  1985, \apjs, 58, 1

\bibitem[\protect\citeauthoryear{{Beucher} \& {Lantuejoul}}{{Beucher} \&
  {Lantuejoul}}{1979}]{Beucher79}
{Beucher} S.,  {Lantuejoul} C.,  1979, in Proceedings Interna- tional Workshop
  on Image Processing, CCETT/IRISA, Rennes, France

\bibitem[\protect\citeauthoryear{{Beucher} \& {Meyer}}{{Beucher} \&
  {Meyer}}{1993}]{Beucher93}
{Beucher} S.,  {Meyer} F.,  1993, {Mathematical Morphology in Image
  Processing}.
Marcel Deker, New York

\bibitem[\protect\citeauthoryear{{Blumenthal}, {da Costa}, {Goldwirth}, {Lecar}
  \& {Piran}}{{Blumenthal} et~al.}{1992}]{Blumenthal92}
{Blumenthal} G.~R.,  {da Costa} L.~N.,  {Goldwirth} D.~S.,  {Lecar} M.,
  {Piran} T.,  1992, \apj, 388, 234

\bibitem[\protect\citeauthoryear{{Bond}, {Kofman} \& {Pogosyan}}{{Bond}
  et~al.}{1996}]{Bond96}
{Bond} J.~R.,  {Kofman} L.,    {Pogosyan} D.,  1996, \nat, 380, 603

\bibitem[\protect\citeauthoryear{{Brunino}, {Trujillo}, {Pearce} \&
  {Thomas}}{{Brunino} et~al.}{2007}]{Brunino07}
{Brunino} R.,  {Trujillo} I.,  {Pearce} F.~R.,    {Thomas} P.~A.,  2007,
  \mnras, 375, 184

\bibitem[\protect\citeauthoryear{{Ceccarelli}, {Padilla}, {Valotto} \&
  {Lambas}}{{Ceccarelli} et~al.}{2006}]{Ceccarelli06}
{Ceccarelli} L.,  {Padilla} N.~D.,  {Valotto} C.,    {Lambas} D.~G.,  2006,
  \mnras, 373, 1440

\bibitem[\protect\citeauthoryear{{Ceccarelli}, {Paz}, {Lares}, {Padilla} \&
  {Lambas}}{{Ceccarelli} et~al.}{2013}]{Ceccarelli13}
{Ceccarelli} L.,  {Paz} D.,  {Lares} M.,  {Padilla} N.,    {Lambas} D.~G.,
  2013, \mnras, 434, 1435

\bibitem[\protect\citeauthoryear{{Chincarini} \& {Rood}}{{Chincarini} \&
  {Rood}}{1975}]{Chincarini75}
{Chincarini} G.,  {Rood} H.~J.,  1975, \nat, 257, 294

\bibitem[\protect\citeauthoryear{{Colberg}, {Pearce} \& et al.}{{Colberg}
  et~al.}{2008}]{Colberg08}
{Colberg} J.~M.,  {Pearce} F.,    et al. 2008, \mnras, 387, 933

\bibitem[\protect\citeauthoryear{{Colberg}, {Sheth}, {Diaferio}, {Gao} \&
  {Yoshida}}{{Colberg} et~al.}{2005}]{Colberg05}
{Colberg} J.~M.,  {Sheth} R.~K.,  {Diaferio} A.,  {Gao} L.,    {Yoshida} N.,
  2005, \mnras, 360, 216

\bibitem[\protect\citeauthoryear{{Colless}, et al. \& {(the 2dFGRS
  Team),}}{{Colless} et~al.}{2001}]{Colless01}
{Colless} M.,  et al.   {(the 2dFGRS Team),} 2001, \mnras, 328, 1039

\bibitem[\protect\citeauthoryear{{Colless}, et al. \& {(the 2dFGRS
  Team),}}{{Colless} et~al.}{2003}]{Colless03}
{Colless} M.,  et al.   {(the 2dFGRS Team),} 2003, VizieR Online Data Catalog,
  7226

\bibitem[\protect\citeauthoryear{{Croton} \& et al.}{{Croton} \&
  et~al.}{2004}]{Croton04}
{Croton} D.~J.,  et al. 2004, \mnras, 352, 828

\bibitem[\protect\citeauthoryear{{Dubinski}, {da Costa}, {Goldwirth}, {Lecar}
  \& {Piran}}{{Dubinski} et~al.}{1993}]{Dubinski93}
{Dubinski} J.,  {da Costa} L.~N.,  {Goldwirth} D.~S.,  {Lecar} M.,    {Piran}
  T.,  1993, \apj, 410, 458

\bibitem[\protect\citeauthoryear{{Einasto}, {Joeveer} \& {Saar}}{{Einasto}
  et~al.}{1980a}]{Einasto80M}
{Einasto} J.,  {Joeveer} M.,    {Saar} E.,  1980a, \mnras, 193, 353

\bibitem[\protect\citeauthoryear{{Einasto}, {Joeveer} \& {Saar}}{{Einasto}
  et~al.}{1980b}]{Einasto80N}
{Einasto} J.,  {Joeveer} M.,    {Saar} E.,  1980b, \nat, 283, 47

\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Contreras} \&
  {Padilla}}{{Forero-Romero} et~al.}{2014}]{Forero2014}
{Forero-Romero} J.~E.,  {Contreras} S.,    {Padilla} N.,  2014, \mnras, 443,
  1090

\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Hoffman}, {Gottl{\"o}ber},
  {Klypin} \& {Yepes}}{{Forero-Romero} et~al.}{2009}]{Forero09}
{Forero-Romero} J.~E.,  {Hoffman} Y.,  {Gottl{\"o}ber} S.,  {Klypin} A.,
  {Yepes} G.,  2009, \mnras, 396, 1815

\bibitem[\protect\citeauthoryear{{Foster} \& {Nelson}}{{Foster} \&
  {Nelson}}{2009}]{Foster09}
{Foster} C.,  {Nelson} L.~A.,  2009, \apj, 699, 1252

\bibitem[\protect\citeauthoryear{{Gottl{\"o}ber}, {{\L}okas}, {Klypin} \&
  {Hoffman}}{{Gottl{\"o}ber} et~al.}{2003}]{Gottlober03}
{Gottl{\"o}ber} S.,  {{\L}okas} E.~L.,  {Klypin} A.,    {Hoffman} Y.,  2003,
  \mnras, 344, 715

\bibitem[\protect\citeauthoryear{{Gregory} \& {Thompson}}{{Gregory} \&
  {Thompson}}{1978}]{Gregory78}
{Gregory} S.~A.,  {Thompson} L.~A.,  1978, \apj, 222, 784

\bibitem[\protect\citeauthoryear{{Hahn}, {Porciani}, {Carollo} \&
  {Dekel}}{{Hahn} et~al.}{2007}]{Hahn07}
{Hahn} O.,  {Porciani} C.,  {Carollo} C.~M.,    {Dekel} A.,  2007, \mnras, 375,
  489

\bibitem[\protect\citeauthoryear{{Hamaus}, {Sutter} \& {Wandelt}}{{Hamaus}
  et~al.}{2014}]{Hamaus14}
{Hamaus} N.,  {Sutter} P.~M.,    {Wandelt} B.~D.,  2014, Physical Review
  Letters, 112, 251302

\bibitem[\protect\citeauthoryear{{Hinshaw} et~al.,}{{Hinshaw}
  et~al.}{2013}]{Hinshaw2013}
{Hinshaw} G.  et~al., 2013, \apjs, 208, 19

\bibitem[\protect\citeauthoryear{{Hoffman}, {Metuki}, {Yepes}, {Gottl{\"o}ber},
  {Forero-Romero}, {Libeskind} \& {Knebe}}{{Hoffman} et~al.}{2012}]{Hoffman12}
{Hoffman} Y.,  {Metuki} O.,  {Yepes} G.,  {Gottl{\"o}ber} S.,  {Forero-Romero}
  J.~E.,  {Libeskind} N.~I.,    {Knebe} A.,  2012, \mnras, 425, 2049

\bibitem[\protect\citeauthoryear{{Hoffman} \& {Shaham}}{{Hoffman} \&
  {Shaham}}{1982}]{Hoffman82}
{Hoffman} Y.,  {Shaham} J.,  1982, \apjl, 262, L23

\bibitem[\protect\citeauthoryear{{Hoyle} \& {Vogeley}}{{Hoyle} \&
  {Vogeley}}{2004}]{Hoyle04}
{Hoyle} F.,  {Vogeley} M.~S.,  2004, \apj, 607, 751

\bibitem[\protect\citeauthoryear{{Icke}}{{Icke}}{1984}]{Icke84}
{Icke} V.,  1984, \mnras, 206, 1P

\bibitem[\protect\citeauthoryear{{Kauffmann} \& {Fairall}}{{Kauffmann} \&
  {Fairall}}{1991}]{Kauffmann91}
{Kauffmann} G.,  {Fairall} A.~P.,  1991, \mnras, 248, 313

\bibitem[\protect\citeauthoryear{{Kirshner}, {Oemler} Jr., {Schechter} \&
  {Shectman}}{{Kirshner} et~al.}{1981}]{Kirshner81}
{Kirshner} R.~P.,  {Oemler} Jr. A.,  {Schechter} P.~L.,    {Shectman} S.~A.,
  1981, \apjl, 248, L57

\bibitem[\protect\citeauthoryear{{Kirshner}, {Oemler} Jr., {Schechter} \&
  {Shectman}}{{Kirshner} et~al.}{1987}]{Kirshner87}
{Kirshner} R.~P.,  {Oemler} Jr. A.,  {Schechter} P.~L.,    {Shectman} S.~A.,
  1987, \apj, 314, 493

\bibitem[\protect\citeauthoryear{{Klypin}, {Trujillo-Gomez} \&
  {Primack}}{{Klypin} et~al.}{2011}]{Klypin11}
{Klypin} A.~A.,  {Trujillo-Gomez} S.,    {Primack} J.,  2011, \apj, 740, 102

\bibitem[\protect\citeauthoryear{{Lavaux} \& {Wandelt}}{{Lavaux} \&
  {Wandelt}}{2012}]{Lavaux12}
{Lavaux} G.,  {Wandelt} B.~D.,  2012, \apj, 754, 109

\bibitem[\protect\citeauthoryear{{Libeskind}, {Hoffman}, {Forero-Romero},
  {Gottl{\"o}ber}, {Knebe}, {Steinmetz} \& {Klypin}}{{Libeskind}
  et~al.}{2013}]{Libeskind13}
{Libeskind} N.~I.,  {Hoffman} Y.,  {Forero-Romero} J.,  {Gottl{\"o}ber} S.,
  {Knebe} A.,  {Steinmetz} M.,    {Klypin} A.,  2013, \mnras, 428, 2489

\bibitem[\protect\citeauthoryear{{Martel} \& {Wasserman}}{{Martel} \&
  {Wasserman}}{1990}]{Martel90}
{Martel} H.,  {Wasserman} I.,  1990, \apj, 348, 1

\bibitem[\protect\citeauthoryear{{Micheletti} et~al.,}{{Micheletti}
  et~al.}{2014}]{Micheletti14}
{Micheletti} D.  et~al., 2014, \aap, 570, A106

\bibitem[\protect\citeauthoryear{{Mu{\~n}oz-Cuartas}, {M{\"u}ller} \&
  {Forero-Romero}}{{Mu{\~n}oz-Cuartas} et~al.}{2011}]{MunozCuartas11}
{Mu{\~n}oz-Cuartas} J.~C.,  {M{\"u}ller} V.,    {Forero-Romero} J.~E.,  2011,
  \mnras, 417, 1303

\bibitem[\protect\citeauthoryear{{M{\"u}ller}, {Arbabi-Bidgoli}, {Einasto} \&
  {Tucker}}{{M{\"u}ller} et~al.}{2000}]{Muller00}
{M{\"u}ller} V.,  {Arbabi-Bidgoli} S.,  {Einasto} J.,    {Tucker} D.,  2000,
  \mnras, 318, 280

\bibitem[\protect\citeauthoryear{{Nadathur} \& {Hotchkiss}}{{Nadathur} \&
  {Hotchkiss}}{2014}]{Nadathur14}
{Nadathur} S.,  {Hotchkiss} S.,  2014, \mnras, 440, 1248

\bibitem[\protect\citeauthoryear{{Neyrinck}}{{Neyrinck}}{2008}]{Neyrinck08}
{Neyrinck} M.~C.,  2008, \mnras, 386, 2101

\bibitem[\protect\citeauthoryear{{Neyrinck}, {Falck} \& {Szalay}}{{Neyrinck}
  et~al.}{2013}]{Neyrinck13}
{Neyrinck} M.~C.,  {Falck} B.~L.,    {Szalay} A.~S.,  2013, ArXiv e-prints

\bibitem[\protect\citeauthoryear{{Padilla}, {Ceccarelli} \& {Lambas}}{{Padilla}
  et~al.}{2005}]{Padilla05}
{Padilla} N.~D.,  {Ceccarelli} L.,    {Lambas} D.~G.,  2005, \mnras, 363, 977

\bibitem[\protect\citeauthoryear{{Pan}, {Vogeley}, {Hoyle}, {Choi} \&
  {Park}}{{Pan} et~al.}{2012}]{Pan10}
{Pan} D.~C.,  {Vogeley} M.~S.,  {Hoyle} F.,  {Choi} Y.-Y.,    {Park} C.,  2012,
  \mnras, 421, 926

\bibitem[\protect\citeauthoryear{{Patiri}, {Betancort-Rijo} \&
  {Prada}}{{Patiri} et~al.}{2006}]{Patiri06a}
{Patiri} S.~G.,  {Betancort-Rijo} J.,    {Prada} F.,  2006, \mnras, 368, 1132

\bibitem[\protect\citeauthoryear{{Patiri}, {Prada}, {Holtzman}, {Klypin} \&
  {Betancort-Rijo}}{{Patiri} et~al.}{2006}]{Patiri06b}
{Patiri} S.~G.,  {Prada} F.,  {Holtzman} J.,  {Klypin} A.,    {Betancort-Rijo}
  J.,  2006, \mnras, 372, 1710

\bibitem[\protect\citeauthoryear{{Paz}, {Lares}, {Ceccarelli}, {Padilla} \&
  {Lambas}}{{Paz} et~al.}{2013}]{Paz13}
{Paz} D.,  {Lares} M.,  {Ceccarelli} L.,  {Padilla} N.,    {Lambas} D.~G.,
  2013, \mnras, 436, 3480

\bibitem[\protect\citeauthoryear{{Platen}, {van de Weygaert} \&
  {Jones}}{{Platen} et~al.}{2007}]{Platen07}
{Platen} E.,  {van de Weygaert} R.,    {Jones} B.~J.~T.,  2007, \mnras, 380,
  551

\bibitem[\protect\citeauthoryear{{Plionis} \& {Basilakos}}{{Plionis} \&
  {Basilakos}}{2002}]{Plionis02}
{Plionis} M.,  {Basilakos} S.,  2002, \mnras, 330, 399

\bibitem[\protect\citeauthoryear{{Regos} \& {Geller}}{{Regos} \&
  {Geller}}{1991}]{Regos91}
{Regos} E.,  {Geller} M.~J.,  1991, \apj, 377, 14

\bibitem[\protect\citeauthoryear{{Ricciardelli}, {Quilis} \&
  {Planelles}}{{Ricciardelli} et~al.}{2013}]{Ricciardelli2013}
{Ricciardelli} E.,  {Quilis} V.,    {Planelles} S.,  2013, \mnras, 434, 1192

\bibitem[\protect\citeauthoryear{{Riebe} et~al.,}{{Riebe}
  et~al.}{2013}]{Riebe11}
{Riebe} K.  et~al., 2013, Astronomische Nachrichten, 334, 691

\bibitem[\protect\citeauthoryear{{Rojas}, {Vogeley}, {Hoyle} \&
  {Brinkmann}}{{Rojas} et~al.}{2005}]{Rojas05}
{Rojas} R.~R.,  {Vogeley} M.~S.,  {Hoyle} F.,    {Brinkmann} J.,  2005, \apj,
  624, 571

\bibitem[\protect\citeauthoryear{{Schaap} \& {van de Weygaert}}{{Schaap} \&
  {van de Weygaert}}{2000}]{Schaap00}
{Schaap} W.~E.,  {van de Weygaert} R.,  2000, \aap, 363, L29

\bibitem[\protect\citeauthoryear{{Shandarin}, {Feldman}, {Heitmann} \&
  {Habib}}{{Shandarin} et~al.}{2006}]{Shandarin06}
{Shandarin} S.,  {Feldman} H.~A.,  {Heitmann} K.,    {Habib} S.,  2006, \mnras,
  367, 1629

\bibitem[\protect\citeauthoryear{{Sheth} \& {van de Weygaert}}{{Sheth} \& {van
  de Weygaert}}{2004}]{Sheth04}
{Sheth} R.~K.,  {van de Weygaert} R.,  2004, \mnras, 350, 517

\bibitem[\protect\citeauthoryear{{Sutter} et~al.,}{{Sutter}
  et~al.}{2015}]{Sutter14}
{Sutter} P.~M.  et~al., 2015, Astronomy and Computing, 9, 1

\bibitem[\protect\citeauthoryear{{Sutter}, {Lavaux}, {Wandelt} \&
  {Weinberg}}{{Sutter} et~al.}{2012}]{Sutter12b}
{Sutter} P.~M.,  {Lavaux} G.,  {Wandelt} B.~D.,    {Weinberg} D.~H.,  2012,
  \apj, 761, 44

\bibitem[\protect\citeauthoryear{{Sutter}, {Lavaux}, {Wandelt}, {Weinberg} \&
  {Warren}}{{Sutter} et~al.}{2014}]{Sutter14a}
{Sutter} P.~M.,  {Lavaux} G.,  {Wandelt} B.~D.,  {Weinberg} D.~H.,    {Warren}
  M.~S.,  2014, \mnras, 438, 3177

\bibitem[\protect\citeauthoryear{{Tikhonov}}{{Tikhonov}}{2006}]{Tikhonov06}
{Tikhonov} A.~V.,  2006, Astronomy Letters, 32, 727

\bibitem[\protect\citeauthoryear{{Tikhonov}}{{Tikhonov}}{2007}]{Tikhonov07}
{Tikhonov} A.~V.,  2007, Astronomy Letters, 33, 499

\bibitem[\protect\citeauthoryear{{van de Weygaert} \& {van Kampen}}{{van de
  Weygaert} \& {van Kampen}}{1993}]{Weygaert93}
{van de Weygaert} R.,  {van Kampen} E.,  1993, \mnras, 263, 481

\bibitem[\protect\citeauthoryear{{von Benda-Beckmann} \& {M{\"u}ller}}{{von
  Benda-Beckmann} \& {M{\"u}ller}}{2008}]{BendaBeckmann08}
{von Benda-Beckmann} A.~M.,  {M{\"u}ller} V.,  2008, \mnras, 384, 1189

\bibitem[\protect\citeauthoryear{{York}, et al. \& {(the SDSS
  Collaboration),}}{{York} et~al.}{2000}]{York00}
{York} D.~G.,  et al.   {(the SDSS Collaboration),} 2000, \aj, 120, 1579

\bibitem[\protect\citeauthoryear{{Zeldovich}, {Einasto} \&
  {Shandarin}}{{Zeldovich} et~al.}{1982}]{Zeldovich82}
{Zeldovich} I.~B.,  {Einasto} J.,    {Shandarin} S.~F.,  1982, \nat, 300, 407

\bibitem[\protect\citeauthoryear{{Zel'dovich}}{{Zel'dovich}}{1970}]{Zeldovich70}
{Zel'dovich} Y.~B.,  1970, \aap, 5, 84

\end{thebibliography}
